---
title: "Simplifying Deep Learning in R with Fast.ai"
description: >
  Fast.ai is an open-source deep learning library that simplifies the process of building and training advanced models for tasks such as computer vision, natural language processing, and tabular data analysis. The library offers a user-friendly interface and powerful tools to achieve state-of-the-art performance. The fast.ai wrapper provides seamless integration with an R environment, allowing users to leverage fast.ai's capabilities and build deep learning models easily. 
author:
  - name: Turgut Abdullayev
    affiliation: Kapital Bank
    affiliation_url: https://www.kapitalbank.az/
slug: keydanagcnn1
date: 2023-03-09
categories:
  - Packages/Releases
output:
  distill::distill_article:
    self_contained: false
    toc: true
preview: images/fastai.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, fig.width = 6, fig.height = 6)
```


## Introduction

Deep learning has revolutionized the field of artificial intelligence by allowing computers to learn from large amounts of data and make accurate predictions or classifications. Fast.ai is an open-source deep learning library that provides a user-friendly interface for building and training deep learning models. It offers state-of-the-art performance on a wide range of tasks, including computer vision, natural language processing, and tabular data analysis. In this blog post, we will focus on how the fast.ai wrapper for R can simplify the process of building and training deep learning models in R. 

```{r}
fastai::install_fastai(gpu = FALSE, cuda_version = '11.6', overwrite = FALSE)
```




